---
title: "test"
output: html_notebook
---
# loading required data
```{r}
dpca1.bcs <- read.csv(here::here("testdata/dpca1_bcs.csv"))
g <- read.csv(here::here("testdata/dpca1_g.csv"))
aca3.bcs <- read.csv(here::here("testdata/aca3_bcs.csv"))
virus <- readRDS(here::here("testdata/b5virus.rds"))
dpca1seurat <- readRDS('D:/BRT/BRT/Data/xc1/DPCA1L1.rds')
```
**be careful**, the orig.ident of seurat must be *sample_region*
```{r}
dpca1seurat@meta.data$orig.ident <- "wqg1_dpca1"
```

the column of the output of match_pattern is *bc, counts*
```{r}
head(g)
# dpca1@coldata <- left_update(dpca1@coldata)
```
to update the counts, we should rename the counts. 
**tva and g** is necessary for analysis, for g-tva linked plasmids, we should 
replicate the result of g and change the colname
```{r}
g <- rename(g,g = counts) %>%
  select(cell,g)
head(g)
```
```{r}
tva <- rename(g,tva = g)
head(tva)
```
# construct obj
Now , we can construct a brtstaretr obj
```{r}
dpca1 <- brtStarter(dpca1.bcs,seuratobj = dpca1seurat,virus = virus,sample = "wqg1",region = "dpca1")
```
and update the tva and g counts into the coldata
```{r}
dpca1@coldata <- left_update(dpca1@coldata,g,by = "cell",treat.na = 0)
dpca1@coldata <- left_update(dpca1@coldata,tva,by = "cell",treat.na = 0)
```
# noise cutoff
First, we can preview the counts of rvcounts and g across each clusters
The **counts of g in ODs** seems abnormal, we'd better avoid ODs while calculating the noise of g
```{r}
brtVlnPlot(dpca1,feature = "rvcounts.raw")
brtVlnPlot(dpca1,feature = "g")
```
Next, we should set a threshold of barcodes. If we level background as NULL,
then, all non-neurons clusters are treated as background, and cluster:Neurons
is singnal. If the cluster name in your hand of Neurons is not Neurons, such as neurons, just change the parameter *signal* to neurons.
Barcodes with counts below median + threshold * IQR of background counts is noise.
```{r}
brtPlotNoise(dpca1,"bc",background = NULL, threshold = 3)
```
**set noise bc with this function**
```{r}
dpca1 <- brtSetNoiseBc(dpca1,threshold = 3)
```

# set cell state and unique bc 
The unique probability of each barcode-carrying virus could be estimated according to the umi counts. For example, barcode *bcA* with P = 0.95 means that while injecting virus, the probablity that only one virus carried *bcA* is 0.95. 
```{r}
dpca1 <- brtSetUniqueVirus(dpca1,P = 0.99)
```
Next, we should set the state of cells (input/starter/naive)
To do this, we should first estimated the threshold, as we disscused above, we'd better avoid ODs while calculating the threshold of g
```{r}
brtPlotNoise(dpca1,feature = "g",background = setdiff(unique(dpca1@coldata$ident),"ODs"),threshold = 3)
```
```{r}
brtPlotNoise(dpca1,feature = "rvcounts.raw",threshold = 3)
```
Now, we know the positive threshold of g/tva, but the negative threshold of tva/g is still unknown. This can be estimated by the probability of barcode positive cells(bcp). If under a threshold, bcp does't increase with  the counts of tva, then this threshold is appropriate.
In this data, bcp is stable... just set the negative threshold as 42...
```{r}
brtPlotInfection(dpca1,tva.c = 42,rv.c = 14)
```
**set cell state here**
```{r}
dpca1 <- brtSetCellState(dpca1,starter = rvcounts.raw > 14 & g >42,input = rvcounts.raw > 14 & g < 42)
```
The last part is select unique barcode. 

There are two standards for unique barcode. 

1. for bc i,across cell 1-j, max(bc i) / sum(bc i) > P (default 0.8) 

These selected bcs are dbcs(dominant bcs) 

2. for dbc i, exist a cell j , dbc i / sum(cell j) > U (default 0.3) 

These selected dbcs are ubcs (unique bcs)
```{r}
dpca1 <- brtSetUniqueBc(dpca1)
```
# construct unity
I do not have a seurat obj of aca3, so I change the region name of dpcall, and disguise it as aca3 obj
```{r}
aca3 <- dpca1
aca3@coldata$region <-"aca3"
aca3@coldata <- select(aca3@coldata,-rvcounts.unique,)
```

```{r}
unity <- brtUnity(list(dpca1),list(aca3))
unity
```



